%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ping Guo} % Your name
\address{No.2006, Xiyuan Ave, West Hi-Tech Zone, 611731} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+86)15520773963 \\ \href{mailto:pingguo625008@gmail.com}{pingguo625008@gmail.com}}


\begin{document}

{\bf Bio}: I'm currently an undergraduate student in Department of Information and Communication Engineering, 
University of Electronic Science and Technology of China, working with Prof.Sheng Wang. My research interest lies in Network Engineering and Machine Learning.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\item \vspace{-1em} {\bf University of Electronic Science and Technology of China, Chengdu} \hfill {\em August 2016 - Present} 
\\ 3rd Year Undergraduate, Honor Class. 
\\IELTS: 7.0(R:8.0 L:7.0 W:6.0 S:6.0)\hfill { Overall Percentage: 86.17 }
\\TOFEL:104(R:29 L:28 S:25 W:22)
\\ Department of Information and Communication Engineering


\item {\bf University of Strathclyde, Glasgow} \hfill {\em August 2018 - January 2019} 
\\ Exchange Student for one semester.\hfill { Overall Percentage: 95.2 }
\\Department of Electronic and Electrical Engineering 


\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{\vspace{-1em} University of Electronic Science and Technology of China}{\em May 2018 - Present}{ Laboratory of Optical Fiber Sensing {\em \&} Communications}{Supervisor: Prof.Wang}
\item \underline{Reconstruction and extension of Pensieve}: This project intends to rebuild Pensieve Neural Network, which is proposed in {\em Neural Adaptive Video Streaming with Pensieve}, and puts it in NS-3 tool to evaluate its performance.
\item \underline{Multi-agent Deep Reinforcement Learning}: Working to propose a framework for multi-agent problem under non-stationary environment. One way is to expand Pensieve model metioned above.
\end{rSubsection}

\begin{rSubsection}{Virginia Polytechnic Institute and State University}{\em December 2018 - Present}{ Member of Secure Localization Team in college of Electrical {\em \&} Computer Engineering}{Supervisor: Prof.Yaling Yang Prof.Gang Wang}
\item \underline{Anti-spoofing Algorithm for GPS}: This project works to put forward an anti-spoofing method for GPS spoofer, which is discussed in {\em All Your GPS Are Belong To Us: Towards Stealthy Manipulation of Road Navigation Systems}.(Another team paper)
\end{rSubsection}

\begin{rSubsection}{University of Electronic Science and Technology of China}{\em March 2018 - May 2018}{ School Project}{Supervisor: Prof.Shang Ma}
\item \underline{Construction of CPU using Vivado}: From bottom to top, building a CPU helps to understand the mechanism of modern computer system. This goes as far as running a binary file in its memory.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Language \ & Python, C++, C, Matlab \\
Software \& Tools & Tensorflow, NS3, Omnet++ \\
\end{tabular}

\end{rSection}


\begin{rSection}{Academic Achievements \& Awards} 
\item[{\bf 2016}] { Won scholarship of University of Electronic Science and Technology of China, Chengdu.}
\item[{\bf 2016}] { Won First Prize of a writing competition of University of Electronic Science and Technology of China, Chengdu.}
\item[{\bf 2016}] { Won Second Place in a talent show of University of Electronic Science and Technology of China, Chengdu.}
\item[{\bf 2017}] { Won Second Prize in Mathematical Modeling Competition Organized by University of Electronic Science and Technology of China, Chengdu.}
\item[{\bf 2018}] { Won Scholarship of Chinese Government to go to Scotland.}
\end{rSection}


\end{document}
